\cvsection{Work Experience}

\input{resume/skills.tex}

\begin{cventries}
  \cventry
    {Agoda} % Job title
	{Senior Software Engineer} % Organization
    {Bangkok, Thailand} % Location
    {September 2023 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		  \item {
				Collaborator on the design and direction of the new Trip product, in Kafka and KTor.
			  }
		  \item {
				Resolved critical backend Scala bugs and improved local testing with Docker Compose and Cucumber.
			  }
		  \item {
				Improved technical on-boarding by consolidating and documenting the complex process on Confluence.
			  }
      \end{cvitems}
    }

  \cventry
    {Aapstaart} % Job title
	{Senior Software Consultant} % Organization
    {Global} % Location
    {January 2022 - August 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		  \item {
			Building data pipelines, ML models, web apps, and automation tools for clients using Python, Pandas, Flutter and NodeJS.
			  }
		  \item {
			Debugged an interactive exhibit for a large Thai convention centre with Arduino, C++, Golang plus software and hardware testing tools.
			  }
      \end{cvitems}
    }


  \cventry
    {Monash University} % Job title
    {Software Developer} % Organization
    {Melbourne, Australia} % Location
    {October 2019 - December 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		  \item {
			 Led, architected and documented cross-team HTML, CSS, Javascript and Python web projects. 
			  }
		  \item {
			 Implemented testing, integration and deployment systems with Bash and Python scripting, git, Docker, GitHub Actions and Ansible. 
			  } 
		  \item {
			 Developed Python packages, a Qt C++ GUI for geographical map processing and visualisation, and 3D geological and geophysical modelling. 
			  }
      \end{cvitems}
    }


  \cventry
    {University of Otago} % Job title
    {Research Assistant} % Organization
    {Dunedin, New Zealand} % Location
    {July 2018 – September 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
			 Researched and implemented a SLAM (simultaneous localisation and mapping) augmented reality system for live sports spectating. 
		}
      \end{cvitems}
    }


%   \cventry
%     {Content Creator} % Job title
%     {Freelance Photographer and Videographer} % Organization
%     {Wellington, New Zealand} % Location
%     {Dec. 2015 – PRESENT} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Photographed events including the National Library’s ’He Tohu’ exhibition, the 2017 New Zealand Comedy festival and many private functions.}
%         \item {Created audio-visual content for local and international comedians and performance venues.}
%       \end{cvitems}
%     }

  % \cventry
  %   {Professional Classical Guitarist and Teacher} % Job title
  %   {New Zealand School of Music} % Organization
  %   {Wellington, New Zealand} % Location
  %   {January. 2013 - Apr. 2018} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {An experienced solo and group musician. Performed at grand events including The Ministry of Youth Development and Japanese Government’s ’Ship for World Youth’ initiative and The United Nations Association of New Zealand’s International Peace Day celebrations.}
		% \item {Taught classical guitar performance and theory to students of all ages using the Suzuki Method.}
  %     \end{cvitems}
  %   }

\end{cventries}
