\cvsection{Projects}

\begin{cventries}
 
  \cventry 
    { Arduino | Golang  } % Empty position
    { AnythingCanBreak\; \href{https://github.com/yohanderose/AnythingCanBreak}{\faGithub\ }	} % Project
	{Bangkok, Thailand} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
		  \item { Interactive art instalment at Queen Sirikit Exhibition Centre, Bangkok. }
		  \item { Sensors arranged around the room feed data to a local network REST API, that plays different sounds depending on where observers are. }
      \end{cvitems}
    }

  \cventry
    { Selenium | Scikit-learn } % Empty position
    {Dat3Bot\; \href{https://github.com/yohanderose/Dat3Bot}{\faGithub\ }	\href{https://yohanderose.dev/dating-with-python}\faBook} % Project
    {Bangkok, Thailand} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item { Desktop application automating the use of popular dating apps like Tinder and Bumble. }
      	\item { Machine learning models that use a) ratios between 3D facial key-points and b) OpenCV demographic models to reliably encode and predict attraction preferences. Cross validating over 98\%.}
      \end{cvitems}
    }

  % \cventry 
  %   { Raspberry Pi | Flask | AWS } % Empty position
	% { Plant-Baby Monitor\; \href{https://github.com/yohanderose/PlantBabyMonitor-IOT}{\faGithub\ \href{https://yohanderose.dev/plant-baby-monitor}\faBook}	} % Project
	% {} % Empty location
  %   {} % Empty date
  %   {
  %     \begin{cvitems} % Description(s) bullet points
  %     	\item { Autonomous indoor plant pot that monitors soil moisture, temperature and humidity and waters itself as needed. }
  %     \end{cvitems}
  %   }

  \cventry 
    {  Flutter | NodeJS | MongoDB } % Empty position
    { Menta\; \href{https://github.com/mentanz/menta-app}{\faGithub\ }	} % Project
	{Wellington, New Zealand} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item { Spaced repetition and active recall cross platform app for high school students. }
		\item{ Trialling in New Zealand, with the goal to expand to Sri Lanka and tackle education inequality. }
      \end{cvitems}
    }

  \cventry
    { Flutter | NodeJS | MongoDB } % Empty position
    {Yakked} % Project
    {Wellington, New Zealand} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item { Personal trainer mobile app that calculates your daily maintenance calories and generates workout programmes. }
      \end{cvitems}
    }


  \cventry
    { React Native (Expo) | NodeJS } % Empty position
    {Badlib} % Project
    {Melbourne, Australia} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item { Cross-platform app for creative writing. Prepares stand up comedy routines by organising bits and sets.}
      \end{cvitems}
    }
    
	% \cventry
	% {Pandas | Scikit-learn | Native Android Development} % Empty position
	% {DataLand 2018 Hackathon} % Project
	% {} % Empty location
	% {} % Empty date
	% {
	% 	\begin{cvitems} % Description(s) bullet points
	% 	\item {2nd place overall, 1st place presentation. Analysed New Zealand Transport Agency crash data and built a mobile app that passively alerts tourists and inexperienced drivers when in crash prone areas.}
	% 	\end{cvitems}
	% }
    \end{cventries}
